Computer Science House Constitution

### 2024-01-30 constitution.tex
Changed last bullet point in 5.F.1 to clarify that only one of the two members has to be present (#142)

	\item When attendance requirements call for the dual directorship position to be present, both dual directorship members are to fulfill the requirements.

>>>>

	\item When attendance requirements call for the dual directorship position to be present, at least one of the members of the dual directorship is to fulfill the requirements.
